Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
here you go paul

\section{Introduction}
\label{sec:introduction}
  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design evacuation routes for at-risk counties in the coastal regions of southern Mississippi. Given that this coastal area is a strong commercial center, the governmental authorities want to minimize the number of unnecessary evacuations. Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as possible. The reasons for this are two-fold. First, this ensures that local businesses can remain open for as long as possible. Second, this ensures that the forecasting reports at the time of the evacuation order are as accurate as possible. Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.

\section{Model Assumptions}
\label{sec:assumptions}
  The MSEMA specified that our plan should be enacted on a per-county basis. As you can see in the following figure, these counties are approximately equally sized:
  \begin{figure}[H]
  \centering
  \includegraphics[width=.5\textwidth]{figures/county_map.jpg}
  \caption{A Map of Counties in the State of Mississippi \cite{county_map}}
  \end{figure}
  As a result of this, we assume that each county can be modeled as a single node in an undirected graph. Then an edge from node $i$ to node $j$ represents that a refugee can directly reach county $j$ from county $i$. Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties. This produced the following graph:
  \begin{figure}[H]
  \centering
  \includegraphics[width=.5\textwidth]{figures/full_undirected-crop.pdf}
  \caption{Undirected Graph Representing Mississippi Counties}
  \end{figure}
  Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between county pairs. In order to capture this homogeneity in the network model, we decided to assign a weight to each edge. A single edge weight then represents a carrying capacity for the amount of travel possible between two counties. As a real world analogy, we assumed that this would correspond to the number of highway lanes traveling from one county to another. Therefore, we were able to assign edge weights across this graph by using the following highway map:
  \begin{figure}[H]
  \centering
  \includegraphics[width=.75\textwidth]{ms_highways.pdf}
  \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
  \end{figure}

\section{Statical Analysis of Historical Hurricane Data}
\label{sec:hurricanes}

@@

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}
    In this model, instead of giving citizens particular evacuation plan, we give them a simple rule.
  \subsection{Parameter Values and Justification}
  \subsection{Results}
  \begin{figure}
    \center
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Hancock County}
    \end{subfigure}~
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Jackson County}
    \end{subfigure}
    \caption{}
  \end{figure}
  \subsection{Strengths and Weaknesses}

@@

\section{Individual Contributions}
\label{sec:contributions}
  \begin{thebibliography}{9}
    \bibitem{county_map}
      \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}

    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}

>>>>

\section{Introduction}
\label{sec:introduction}
  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design evacuation routes for at-risk counties in the coastal regions of southern Mississippi. Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations. Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as safely possible. The reasons for this are two-fold. First, this ensures that local businesses can remain open for as long as possible. Second, this ensures that the forecasts at the time of the evacuation order are as accurate as possible. Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.

\section{Network Representation of Mississippi}
\label{sec:representation}
  \par
    The MSEMA specified that our plan should be enacted on a per-county basis. As you can see in the following figure, these counties are approximately equally sized. As a result of this, we assume that each county can be modeled as a single node in a bidirectional graph. Then an edge from node $i$ to node $j$ represents an available evacuation route from county $i$ to county $j$. Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties that are connected by roads:
  \begin{figure}[H]
    \center
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=.9\linewidth]{figures/county_map.jpg}
      \caption*{A Map of Counties in the State of Mississippi \cite{county_map}}
    \end{subfigure}~
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/full_undirected-crop.pdf}
      \caption*{Undirected Graph Representing Mississippi Counties}
    \end{subfigure}
    \caption*{}
  \end{figure}
  \par
    In all of our models we assume that highways are the only means of evacuation. Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between county pairs. In order to capture this homogeneity in the network model, we decided to assign weights to every edge. Then a single edge weight represents a carrying capacity for the amount of travel possible between two counties. For a real-world mapping, we assume that this would correspond to the total number of highway lanes spanning two counties. Therefore, we were able to assign edge weights across this graph by using the following highway map:
  \begin{figure}[H]
  \centering
  \includegraphics[width=.5\textwidth]{ms_highways.pdf}
  \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
  \end{figure}
  \par
    In this figure, the thick black lines represent four lane highways while the red lines represent two lane highways. We assume that despite the ensuing panic, evacuees still travel along the right side of the highway, even if this means lanes going the other way (towards the hurricane) are underutilized. Therefore, for every thick black line spanning two counties, the appropriate edge in the graph gains two additional lanes, whereas red lines add one lane. Summing the contributions of all lanes a pair of counties therefore gives us an single edge weight in the graph.
  \newline
  \par
    We assume that there is a fixed spacing between every car on every highway. Then all cars travel at the same speed, and the density of cars is uniform along the entire length of every highway. This determines a fixed flow rate per edge capacity, and allows us to compute the number of cars that can travel to another county in a given time interval.

\section{Historical Hurricane Trends}
\label{sec:hurricanes}
  Go northwest

@@

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}

  \subsection{Parameter Values and Justification}
  \subsection{Results}
  \begin{figure}
    \center
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Hancock County}
    \end{subfigure}~
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Jackson County}
    \end{subfigure}
    \caption{}
  \end{figure}
  \subsection{Strengths and Weaknesses}

@@

\section{Individual Contributions}
\label{sec:contributions}
  \begin{thebibliography}{9}
    \bibitem{county_map}
      \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
    \bibitem{ms_highways}
      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
